Pool Model

### 2023-12-20 pool_model.tex
new simulation run with corrected intracellular reactions
adapt parameters to new run
display more json files in supplement

        &                           & $\lambda_A$   & $0.008$\unit{\per\minute}\\

@@

@@

        Total volume     & $G_\text{max}$         & $2.0\cdot 10^5$\unit{\micro\metre\cubed}

@@

    \caption{The list of the initial values of the system.}

@@

c1.set_pos(&(old_pos + offset));
c2.set_pos(&(old_pos - offset));
\end{lstlisting}
\caption{
    Sample code for dividing one bacteria cell into two.
}
\end{listing}
%
%
\end{document}

>>>>

        &                           & $\lambda_A$   & $0.0025$\unit{\per\minute}\\

@@

        & Production                & $b$           & $0.1$\unit{\per\minute}\\

@@

        & Inhibition                & $\nu_I$       & $0.1$\unit{\micro\metre\cubed\per\mol}\\
        Total volume                & $G_\text{max}$& $2.0\cdot 10^5$\unit{\micro\metre\cubed}

@@

        List paramters for both models.
        Specifying all parameters here would requrie a much larger table.
        For the full information, we refer to the supplementary material~\ref{sec:supplement-full-parameters}.

@@

c1.set_pos(&(old_pos + offset));
c2.set_pos(&(old_pos - offset));
\end{lstlisting}
\caption{
    Sample code for dividing one bacteria cell into two.
}
\end{listing}
%
%
% ................................................................................................
\subsection{Full List of Parameters}
\label{sec:supplement-full-parameters}
\begin{listing}
\begin{lstlisting}[language=json]
{
    "diffusion_constants": [
        15.0,
        15.0
    ],
    "initial_concentrations": [
        2.0,
        0.0
    ],
    "size": 1000.0,
    "n_voxels": null
}
\end{lstlisting}
\caption{
    The \texttt{domain.json} file specifying initial values of the domain.
}
\end{listing}
%
\begin{listing}
\begin{lstlisting}[language=json]
{
    "random_seed": 1,
    "n_times": 20001,
    "dt": 0.5,
    "t_start": 0.0,
    "save_interval": 500,
    "n_threads": 8,
    "show_progressbar": true,
    "save_path": "out/pool_model",
    "save_add_date": true
}
\end{lstlisting}
\caption{
    The \texttt{meta\_params.json} file specifying all parameters not directly related to the simulation content.
    These settings do not represent any model-specific properties but rather generic ones such as time-span or number of threads.
}
\end{listing}
%
\begin{listing}
\begin{lstlisting}[language=json]
{
    "mechanics": {
        "pos": [
        142.85714285714286,
        142.85714285714286
        ],
        "vel": [
        0.0,
        0.0
        ],
        "damping_constant": 0.5,
        "mass": 7.704755982928968
    },
    "cycle": {
        "volume_division_threshold": 14.137166941154069,
        "lag_phase_transition_rate_1": 0.005,
        "lag_phase_transition_rate_2": 0.0025
    },
    "cellular_reactions": {
        "potential_strength": 0.5,
        "food_to_volume_conversion": 0.1,
        "lag_phase_active": true,
        "species": "S1",
        "cell_volume": 7.0685834705770345,
        "uptake_rate": 0.01,
        "inhibition_production_rate": 0.1,
        "inhibition_coefficient": 0.1
    },
    "interactionextracellulargradient": null
}
\end{lstlisting}
\caption{
    The first entry of the \texttt{initial\_cells.json} file which defines every individual particle present in the simulation initially.
}
\end{listing}
%
%
\end{document}
